\documentclass{prometheus_cv}
\usepackage[utf8]{inputenc}
\usepackage[left=1.5in, right=0.5in, bottom=0.25in, top=0.25in]{geometry}		% width=5.3in, height=10in, top margin=2cm on each page

\usepackage{xcolor}																				  % define some colors
\definecolor{highlight}{HTML}{283559}
\definecolor{highlight2}{HTML}{1A2640}
\definecolor{link}{HTML}{9b3154}

\usepackage{lipsum}
\usepackage{siunitx}							% package to properly set units
\usepackage{fontawesome5}						% package for icons (see list of available icons here: http://mirrors.ibiblio.org/CTAN/fonts/fontawesome5/doc/fontawesome5.pdf)
\usepackage[super]{nth}							% when you write \nth{2} you get a nice superscript
\usepackage[								% coloring of links
	colorlinks = true,
	linkcolor = highlight,
	urlcolor = highlight,
	citecolor= highlight
]{hyperref}

\usepackage{fontspec}							% package to change fonts				
\setmainfont[]{Charter}
\newfontfamily\GaramondLight{Charter}
\newcommand\textlf[1]{{\GaramondLight#1}}

\newcommand{\highlight}[1]{\textcolor{highlight}{\textbf{#1}}}		% highlight text as bold and with the highlight color defined above
\newcommand{\ec}{\textsuperscript{\textdagger}}								% Equal contribution dagger


% define the header and (not) footer %
\usepackage{fancyhdr}																		  
\fancyhf{}
\rhead{Curriculum Vit\ae}
\lhead{Prometheus Fire}
\rfoot{Page \thepage}
\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0pt}

\begin{document}
\thispagestyle{empty}					% Turn off header and footer for the first page
\pagestyle{fancy}			 		% For the rest of the pages switch to the fancy page style defined just above the document begin

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%% TITLE %%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\centering 

\begin{Large} 
   Richard Posert
\end{Large}

\vspace*{0.25em}
\begin{scshape}
   \begin{footnotesize}
		 \textcolor{highlight2}{CryoEM $\cdot$ Biochemistry $\cdot$ Computation}
		 
		 \vspace*{-1ex}
		 \textcolor{highlight2}{Scientific communication $\cdot$ Data visualization and design}
   \end{footnotesize}
\end{scshape}
\vspace*{0.25em}

\begin{footnotesize}
   \begin{tiny}\faHome\end{tiny}~\href{https://resume.posertinlab.com}{
	   posertinlab.com
   }
   \quad \begin{tiny}\faEnvelope[regular]\end{tiny}~\href{mailto:rich@posertinlab.com}{%
	   rich@posertinlab.com
   } 
   \quad \begin{tiny}\faMobile*\end{tiny}~\href{tel:9492743495}{
	   (949) 274-3495
   }
   \quad \begin{tiny}\faGraduationCap\end{tiny}~\href{https://scholar.google.com/citations?user=eNNSP4gAAAAJ&hl=en}{
		Google Scholar
	   }

\end{footnotesize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%% EDUCATION %%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
\datedsubsection{2018 -- 2023}
	{%
		Vollum Institute, OHSU, Portland, OR}
	{%
		\textbf{Ph.D.}~in biochemistry and molecular biology}
	{%
	\begin{itemize}
		\item Extensive experience with cryoEM single-particle analysis, focused on small, flexible membrane proteins. Improved best map of ENaC extracellular domain from 3.1 to 2.4 \AA{}.
		\item Developed multiple functional assays and automated processing and presentation scripts for each.
		\item Developed several software tools, including \href{https://doi.org/10.1371/journal.pone.0280255}{Appia}, a chromatography suite; \href{https://github.com/PlethoraChutney/exawatcher}{Exawatcher}, a RELION job monitor; and \href{https://github.com/PlethoraChutney/Mortimer}{Mortimer}, a real-time cryoEM screening processor and organizer.
	\end{itemize}
	}

\datedsubsection{2011 -- 2015}
		{%
			Reed College, Portland, OR}
		{%
			\textbf{BA}~in biochemistry and molecular biology}
		{%
		Thesis in Janis Shampay's lab: \textit{Structural Characteristics of the PinX1 Telomerase Inhibitory Domain}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%% PUBLICATIONS %%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Publications}
\newcounter{publicationCounter}			% We set a publication counter, we can continue counting the publications when switching from conferences to workshop etc.

\begin{enumerate}
	\item \textbf{Richard Posert}, Isabelle Baconguis. \textit{Appia: Simpler chromatography analysis and visualization}. In \textit{PLoS ONE}, 2023. doi: \href{https://doi.org/10.1371/journal.pone.0280255}{10.1371/journal.pone.0280255}
	\item Sigrid Noreng, \textbf{Richard Posert}, Arpita Bharadwaj, Alexandra Houser, Isabelle Baconguis. \textit{Molecular principles of assembly, activation, and inhibition in epithelial sodium channel}. In \textit{eLife}, 2020. doi: \href{https://doi.org/10.7554/eLife.59038}{10.7554/eLife.59038}
	\item Johannes Elferich, \textbf{Rich Posert}, Craig Yoshioka, and Eric Gouaux. \textit{HOTSPUR: A Real-time Interactive Preprocessing System for Cryo-EM Data}. In \textit{Microscopy and Microanalysis}, 2019. doi: \href{https://doi.org/10.1017/S1431927619006792}{10.1017/S1431927619006792}
	\item Sigrid Noreng, Arpita Bharadwaj, \textbf{Richard Posert}, Craig Yoshioka, Isabelle Baconguis. \textit{Structure of the human epithelial sodium channel by cryo-electron microscopy}. In \textit{eLife}. doi: \href{https://doi.org/10.7554/eLife.39340}{10.7554/eLife.39340}
	%
	\setcounter{publicationCounter}{\value{enumi}}	% Remember the counts
\end{enumerate}

\subsection{In preparation (draft available upon request)}
\begin{enumerate}
	\setcounter{enumi}{\value{publicationCounter}}
	\item \textbf{Richard Posert}, Arpita Bharadwaj, Isabelle Baconguis. \textit{Activating conditions of ENaC do not produce expected conformational changes}.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%% SERVICE %%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Teaching and Service}
\datedsubsection{2022}
{Co-instructor}
{NEUS 619, Neuroscience Graduate Program, OHSU}
{%
	I was one of two instructors for the required course on scientific speaking.
	I led classes covering topics including talk writing, slide design, audience management, and Q\&A sessions.}

\datedsubsection{2019 -- 2022}
{Guest lecturer}
{Biochemistry lectures}
{%
	I have been invited to give guest lectures for \textit{Chem330 - Structural Biochemistry} at Lewis and Clark and the structural biochemistry course at Reed.}

\datedsubsection{2018--2020}
{Lead organizer, bargaining team, executive board}
{AFSCME Local 402}
{%
	In my role as a lead organizer, I helped grow our union through one-on-one conversations from eight people to over 300, and built systems to manage that growth. I also organized, processed, and communicated the results of issue and priority surveys. As a member of the bargaining team, I was a member of a team of four that wrote and negotated a contract worth, in total, over \$3,000,000 and coordinated several teams focused on individual issues. As a member of the first e-board, I helped build a governing structure focused on equity and representation.}

\datedsubsection{2019}
{Teaching assistant}
{CONJ 661 - Structure and Function of Biological Molecules}
{%
	Coordinated and ran study sessions, journal clubs, and review for the required structural biochemistry course at OHSU.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%% HONORS and SCHOLARSHIPS %%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Awards and Funding}
\datedsubsectionnarrow{2019}
{%
	NIH T32GM071338-13}
{%
	Program in Enhanced Research Training}
{}

\datedsubsectionnarrow{2019}
{%
	AFSCME}
{%
	Emerging Leader}
{}

\end{document}
